DraftDataAnalysis

### 2023-05-07 DraftDataAnalysis.Rmd
Add files via upload

```{r}
draftPick %>%
  filter(Draft > 1993) %>%
  group_by(Rnd) %>%
  summarise(averagewAV = mean(wAV))
```
```{r}
draftPick %>%
  group_by(Pick) %>%
  summarise(averagewAV = mean(wAV))
```

@@

When should positions really be drafted?
```{r}
draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Draft < 2011) %>%
  filter(Rnd == 1) %>%
  group_by(Pos) %>%
  summarize(avgwAV = mean(wAV)) %>%
  arrange(desc(avgwAV))
```

Position: T
```{r}
draftT = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "T") %>%
  filter(Draft < 2011) %>% 
  arrange(Pick)

@@

draftT %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )

reg = lm(draftT$wAV~log(draftT$Pick))

b = predict(reg)
PickValue = tibble(Pick = 1:350, wAV = b)
PickValue = PickValue %>%
  filter(Pick < 256)
PickValue
```
```{r}
draftT = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "T") %>%
  filter(Draft < 2011)

draftT %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )

draftQB = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "QB") %>%
  filter(Draft < 2011)

draftDE = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "DE") %>%
  filter(Draft < 2011)
```
```{r}
draftPos = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == c("T", "QB", "DE")) %>%
  filter(Draft < 2011)

draftPos %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_jitter(aes(draftT$Pick, draftT$wAV), colour = "red") + 
  stat_smooth(aes(draftT$Pick, draftT$wAV, col = "red"),
              method = lm,
              formula = y~log(x),
              se = TRUE,
              ) +
  geom_jitter(aes(draftQB$Pick, draftQB$wAV), colour = "blue") + 
  stat_smooth(aes(draftQB$Pick, draftQB$wAV, col = "blue"),
              method = lm,
              formula = y~log(x),
              se = TRUE,
              )
```
```{r}
draft %>%
  filter(Player == "Joe Webb")
```

>>>>

```{r}
roundPick = draftPick %>%
  filter(Draft > 1993) %>%
  group_by(Rnd) %>%
  summarise(averagewAV = mean(wAV))
roundPick
```
```{r}
draftPick %>%
  group_by(Pick) %>%
  summarise(averagewAV = mean(wAV))
```

@@

When should positions really be drafted?
AveragewAV for first round talent per Position
```{r}
draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Draft < 2011) %>%
  filter(Rnd == 1) %>%
  group_by(Pos) %>%
  summarize(avgwAV = mean(wAV)) %>%
  arrange(desc(avgwAV))
```

Position: T
wAV as the Draft goes on and then the wAV per each player per position in draft
```{r}
draftT = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "T") %>%
  filter(Draft < 2011) %>% 
  arrange(Pick)

@@

#wAV per Pick per tackle
p = draftT %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftTOrder = draftT %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftTOrder) 
reg1 = lm(draftTOrder$wAV~draftTOrder$PosDraft)
reg2 = lm(draftTOrder$wAV~log(draftTOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftTOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: QB
```{r}
draftQB = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "QB") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftQB) 
reg1 = lm(draftQB$wAV~draftQB$Pick)
reg2 = lm(draftQB$wAV~log(draftQB$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftQB %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftQBOrder = draftQB %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftQBOrder) 
reg1 = lm(draftQBOrder$wAV~draftQBOrder$PosDraft)
reg2 = lm(draftQBOrder$wAV~log(draftQBOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftQBOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: DE
```{r}
draftDE = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "DE") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftDE) 
reg1 = lm(draftDE$wAV~draftDE$Pick)
reg2 = lm(draftDE$wAV~log(draftDE$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftDE %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftDEOrder = draftDE %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftDEOrder) 
reg1 = lm(draftDEOrder$wAV~draftDEOrder$PosDraft)
reg2 = lm(draftDEOrder$wAV~log(draftDEOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftDEOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: DT
```{r}
draftDT = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "DT") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftDT) 
reg1 = lm(draftDT$wAV~draftDT$Pick)
reg2 = lm(draftDT$wAV~log(draftDT$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftDT %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftDTOrder = draftDT %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftDTOrder) 
reg1 = lm(draftDTOrder$wAV~draftDTOrder$PosDraft)
reg2 = lm(draftDTOrder$wAV~log(draftDTOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftDTOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: C
```{r}
draftC = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "C") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftC) 
reg1 = lm(draftC$wAV~draftC$Pick)
reg2 = lm(draftC$wAV~log(draftC$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftC %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftCOrder = draftC %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftCOrder) 
reg1 = lm(draftCOrder$wAV~draftCOrder$PosDraft)
reg2 = lm(draftCOrder$wAV~log(draftCOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftCOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: G
```{r}
draftG = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "G") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftG) 
reg1 = lm(draftG$wAV~draftG$Pick)
reg2 = lm(draftG$wAV~log(draftG$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftG %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftGOrder = draftG %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftGOrder) 
reg1 = lm(draftGOrder$wAV~draftGOrder$PosDraft)
reg2 = lm(draftGOrder$wAV~log(draftGOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftGOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: LB
```{r}
draftLB = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "LB") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftLB) 
reg1 = lm(draftLB$wAV~draftLB$Pick)
reg2 = lm(draftLB$wAV~log(draftLB$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftLB %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftLBOrder = draftLB %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftLBOrder) 
reg1 = lm(draftLBOrder$wAV~draftLBOrder$PosDraft)
reg2 = lm(draftLBOrder$wAV~log(draftLBOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftLBOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: RB
```{r}
draftRB = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "RB") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftRB) 
reg1 = lm(draftRB$wAV~draftRB$Pick)
reg2 = lm(draftRB$wAV~log(draftRB$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftRB %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftRBOrder = draftRB %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftRBOrder) 
reg1 = lm(draftRBOrder$wAV~draftRBOrder$PosDraft)
reg2 = lm(draftRBOrder$wAV~log(draftRBOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftRBOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: DB
```{r}
draftDB = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "DB") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftDB) 
reg1 = lm(draftDB$wAV~draftDB$Pick)
reg2 = lm(draftDB$wAV~log(draftDB$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftDB %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftDBOrder = draftDB %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftDBOrder) 
reg1 = lm(draftDBOrder$wAV~draftDBOrder$PosDraft)
reg2 = lm(draftDBOrder$wAV~log(draftDBOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftDBOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: WR
```{r}
draftWR = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "WR") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftWR) 
reg1 = lm(draftWR$wAV~draftWR$Pick)
reg2 = lm(draftWR$wAV~log(draftWR$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftWR %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftWROrder = draftWR %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftWROrder) 
reg1 = lm(draftWROrder$wAV~draftWROrder$PosDraft)
reg2 = lm(draftWROrder$wAV~log(draftWROrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftWROrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```
Position: TE
```{r}
draftTE = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "TE") %>%
  filter(Draft < 2011) %>%
  arrange(Pick)

attach(draftTE) 
reg1 = lm(draftTE$wAV~draftTE$Pick)
reg2 = lm(draftTE$wAV~log(draftTE$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p = draftTE %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p
p2 = ggplot_build(p)
p2$data[[2]]

draftTEOrder = draftTE %>%
  group_by(Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft)

attach(draftTEOrder) 
reg1 = lm(draftTEOrder$wAV~draftTEOrder$PosDraft)
reg2 = lm(draftTEOrder$wAV~log(draftTEOrder$PosDraft))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

p3 = draftTEOrder %>%
  ggplot(aes(x=PosDraft, y=wAV)) +
  geom_point() +
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )
p3
p4 = ggplot_build(p3)
p4$data[[2]]
```

```{r}
draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Draft < 2011) %>%
  group_by(Pos) %>%
  summarize(avgwAV = mean(wAV)) %>%
  arrange(desc(avgwAV))

draft %>%
  filter(Draft < 2011) %>%
  group_by(Pos) %>%
  summarize(avgwAV = mean(wAV))
draft %>%
  filter(Pos == "DL")
```
